Clustering: A pipeline to analyse time-course gene expression data

### 2019-05-07 scripts/03_clustering.Rmd
Better text + colors
FIX clustering

# Then rank by fisher's p-value and take max the number of genes of interest
# Filter out q-values for the pvalues table
fishers_pval = moanin:::fisher_method(pvalues)
fishers_qval = stats::p.adjust(fishers_pval)
genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])

@@

>>>>

# Then rank by fisher's p-value and take max the number of genes of interest
# Filter out q-values for the pvalues table
fishers_pval = moanin:::fisher_method(pvalues)
fishers_qval = stats::p.adjust(fishers_pval)
genes_to_keep = names(sort(fishers_pval))
if(length(genes_to_keep) > n_genes_to_keep){
    genes_to_keep = genes_to_keep[1:n_genes_to_keep]
}

@@

The consensus clustering method suggest that the most stable is $k=2$, which
separates over-expressed genes from under-expressed genes. While it is indeed
a very stable clustering, it does not capture the range of gene expression
patterns present in the data.
